Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-20 prop_iop.tex
few changes here and there

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed. In a strict computational
or experimental setting, one should question the reliance of the
definition of probability space on the uncountable and
uncomputable real
interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
This interval includes numbers like
$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\pi / 4$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

@@

@@

\amr{Another: the calculus of probabilities requires all probabilities to
be \emph{coherent}. But given limited resources, a user can only
approximate the probabilities and the approximation may not be
completely coherent in the ideal sense.}

>>>>

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed.

@@

In a strict computational or experimental setting, one should question
the reliance of the definition of probability space on the uncountable
and uncomputable real
interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
This interval includes numbers like $0.h_{1}h_{2}h_{3}\ldots$ where
$h_{i}$ is 1 or 0 depending on whether Turing machine
$\mathit{TM}_{i}$ halts or not. Such numbers cannot be computed. This
interval also includes numbers like $\pi / 4$ which can only be
computed with increasingly large resources as the precision
increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

@@

Another way to re-express the above observations is that the calculus
of probabilities requires all probabilities to be \emph{coherent}
(e.g., the probability of the union of two disjoint events is the sum
of their probabilities). But given limited resources, the calculation
of a probability measure can only be approximate and hence the
probabilities cannot be absolutely guaranteed to be coherent in the
ideal sense.
